Where and Why Do Models Fail? A Visualization Tool for Analyzing and Interpreting Natural Language Inference

### 2018-03-06 paper/paper_entailVis.tex
fix bibtex
grammar fix
update title
fix resizing
add perturbation motiation

\documentclass[journal]{vgtc}                % final (journal style)
%\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% Paper title.
\title{Where and Why Does the Model Failed?  A Visual Analytics Tool for Debugging and Interpreting Text Entailment Model}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, attention, and the prediction.
} % end of abstract

@@

\bibliography{template}
\end{document}

>>>>

% \documentclass[journal]{vgtc}                % final (journal style)
\documentclass[review,journal]{vgtc}         % review (journal style)
%\documentclass[widereview]{vgtc}             % wide-spaced review
%\documentclass[preprint,journal]{vgtc}       % preprint (journal style)

@@

%% Paper title.
\title{Where and Why Do Models Fail?  A Visualization Tool for Analyzing and Interpreting Natural Language Inference}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network based models have reset the state-of-the-art performance for nearly all linguistic tasks in natural language processing. The disruptive progress also brings enormous challenges.
The opaque nature of neural network model leads to hard to debug system and difficult to interpret mechanisms. In this work, we use textual entailment task as an example to illustrate how a flexible visualization system can not only help NLP researchers quickly identify the potential limitation of a model, but also facilitate the interpretation the model mechanisms by allowing interactive exploration of the interplay between model input, model inner states, and the prediction.
} % end of abstract

@@

\bibliography{entailVis.bib}
\end{document}

### 2018-03-06 paper/perturbation.tex
add perturbation motiation

\section{Analysis of the Model Via Perturbation}

@@

\subsection{Input Perturbation}
\begin{itemize}
    \item Just looking at the failure cases is not enough, the prediction maybe correct for the wrong reason
    \item sensitivity of the model with respect of
\end{itemize}

@@

\subsection{Attention Perturbation}

\subsection{Prediction Perturbation}

>>>>

\section{Error Analysis Via Input Perturbation}

Understand where and how does a model fail is the first step to improve the
model performance.
Prediction accuray, i.e., the percentage of the correct prediction according to
the ground truth label, is the standard technique to verify the performance
of a model on a given supervised task.
%
The accuracy alone does not tell us the whole story, it provides no
information on the specific example and the condition that lead to a failure.
%
Often, the user need to examine individual failure examples to dignostic the
issue and identify the weakness of the model.
%
However, the model may be unstable and generate the right prediction for the wrong
reason (e.g., by picking up noise in the data that is not the intended features),
therefore, we are likely to miss some important failure condition by just looking
at the failure cases.
%
An in depth analysis of the error made by the model requires the verification of
the robustness of the prediction.
%
One powerful tool to assess robustness is through the application of small
perturbation in the input and then check the variation of the prediction.
%
For example, we can replace noun and verb in the sentences with words of
similar/same meaning, such an operation is often carried out by domain experts
(subconsciously) when they try to figure out the potential issue of a model.
%
In another work, the perturbation of the input allow us to do a sensitivity
analysis on the prediction.
%
In this work, we introduce an synonyms perturbation scheme that automatically
generate the perturbation and generate the prediction and summarized the prediction
variation.
%

\begin{itemize}
    \item perturbation prediction change ratio
    \item prediction distance (KL divergines) to original prediction
    \item attention change distance
\end{itemize}

@@

% \subsection{Input Perturbation}

@@

% \subsection{Attention Perturbation}

% \subsection{Prediction Perturbation}
